---
title: "Visualizing Large Distributions"
author: "Payton Stastny"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)

```
## Data Given
```{r load_data}
# Use this R-Chunk to import all your datasets!
nycflights13::flights
```
## Univariate 1

The first univariate display i wanted to look at was the number of flights each carrier has.
```{r plot_data.1}
# Use this R-Chunk to clean & wrangle your data!
ggplot(data = nycflights13::flights) +
  geom_bar(mapping = aes(x = fct_infreq(carrier)))
```

## Univariate 2

The second univariate display i wanted to look at was the amount of delayed departures

```{r plot_data.2}
# Use this R-Chunk to plot & visualize your data!

ggplot(data = nycflights13::flights,
      aes(x = dep_delay)) +
  geom_histogram(
    color = "white",
    binwidth = 10) +
  coord_cartesian(
    xlim = c(-25, 250))
```

## Bivariate Graph

This zoomed in box plot graph shows us the quartiles in which carriers have late departures or on time departures.

```{r plot_data.3}
# Use this R-Chunk for bivariate plot
ggplot(data = nycflights13::flights) +
  aes(x = fct_reorder(carrier, dep_delay, na.rm = TRUE)) +
  aes(y = dep_delay) +
 geom_boxplot() +
  coord_cartesian(ylim = c(-50,250))
```

## Conclusions

From the data that i picked out and summerized into these graphs, i have been able to find out identify what carriers have more departure delays than others and using the boxplot, i can know what percentage of carriers flights have delays or are ahead of schedule on average. Like we can see that 75% of HA and US have flights ahead of schedule.